Liveness-Based Garbage Collection for Lazy Languages

### 2016-05-02 paper/paper.tex
saved space
fixed plots in arxiv paper deleted non-essential files in paper.

%\newcommand{\mycomment}[1]{{\color{Myblue}{#1}}}
\newcommand{\added}[1]{{\color{Myblue}{#1}}}
%\newcommand{\added}[1]{#1}
%\newcommand{\todelete}[1]{}%{\color{Myred}{#1}}}
%\newcommand{\warning}[1]{{\color{Myred}{#1}}}
%\newcommand{\warning}[1]{}
%\newcommand{\blankout}[1]{}

@@

A notion  that generalizes liveness  is {\em demand}.   Whereas liveness
gives the patterns of future uses of a variable, demand represents the
future uses of the value of an expression.  The demand on an expression
$e$   is   also   a   set    of   access   paths---the   subset   of
$\{\acar,\acdr\}^\ast$ which the  context of $e$ may  explore of $e$'s
result.   To see  the need  for demands,  consider the expression
$(\LET~x\leftarrow  (\CDR~y)~\IN~   (\SRETURN~x))$.   Assume   that  the
context of this expression places  the demand $\lbrace \epsilon, \acar
\rbrace$. Since the  value of the expression is the  value of $x$, the
demand translates to the liveness  $[x \mapsto \lbrace \epsilon, \acar
  \rbrace]$.   Due  to  the  \LET\   definition  which  binds  $x$  to
$(\CDR~y)$, the liveness of $x$  now becomes the demand on $(\CDR~y)$.
This, in  turn, generates  the liveness $\lbrace  y.\epsilon, y.\acdr,
y.\acdr\acar  \rbrace$.   These are  the $y$-rooted  accesses
required to  explore $\lbrace  \epsilon, \acar  \rbrace$ paths  of the
result of $(\CDR~y)$.
%% As an  analogy with classical  (strong) liveness analysis,  $y$ and
%% $z$ are live at the entry $\pi: x:=y+z$, if and only if $x$ is live
%% at  exit  of $\pi$.   In  our  terminology, the  liveness  $\lbrace
%% \epsilon\rbrace $ of $x$ at the  exit from $\pi$ becomes the demand
%% on  $y+z$,  and  this,  in turn  generates  the  liveness  $\lbrace
%% y.\epsilon, z.\epsilon \rbrace$ at the entry of $\pi$.

@@

\section*{Acknowledgement}
We would like to thank the anonymous referees for their valuable suggestions. We thank 
Evgeny Kapun for his suggestions regarding the undecidability proof.

>>>>

%\newcommand{\mycomment}[1]{{\color{Myblue}{#1}}}
%\newcommand{\added}[1]{{\color{Myblue}{#1}}}
\newcommand{\added}[1]{#1}
%\newcommand{\todelete}[1]{}%{\color{Myred}{#1}}}
%\newcommand{\warning}[1]{{\color{Myred}{#1}}}
%\newcommand{\warning}[1]{}
%\newcommand{\blankout}[1]{}

@@

A notion  that generalizes liveness  is {\em demand}.   Whereas liveness
gives the patterns of future uses of a variable, demand represents the
future uses of the value of an expression.  The demand on an expression
$e$   is   also   a   set    of   access   paths
%---the   subset   of $\{\acar,\acdr\}^\ast$ 
which the  context of $e$ may  explore of $e$'s
result.   To see  the need  for demands,  consider the expression
$(\LET~x\leftarrow  (\CDR~y)~\IN~   (\SRETURN~x))$.   Assume   that  the
context of this expression places  the demand $\lbrace \epsilon, \acar
\rbrace$. Since the  value of the expression is the  value of $x$, the
demand translates to the liveness  $[x \mapsto \lbrace \epsilon, \acar
  \rbrace]$.   Due  to  the  \LET\   definition  which  binds  $x$  to
$(\CDR~y)$, the liveness of $x$  now becomes the demand on $(\CDR~y)$.
This, in  turn, generates  the liveness $\lbrace  y.\epsilon, y.\acdr,
y.\acdr\acar  \rbrace$.   These are  the $y$-rooted  accesses
required to  explore $\lbrace  \epsilon, \acar  \rbrace$ paths  of the
result of $(\CDR~y)$.
%% As an  analogy with classical  (strong) liveness analysis,  $y$ and
%% $z$ are live at the entry $\pi: x:=y+z$, if and only if $x$ is live
%% at  exit  of $\pi$.   In  our  terminology, the  liveness  $\lbrace
%% \epsilon\rbrace $ of $x$ at the  exit from $\pi$ becomes the demand
%% on  $y+z$,  and  this,  in turn  generates  the  liveness  $\lbrace
%% y.\epsilon, z.\epsilon \rbrace$ at the entry of $\pi$.

@@

\section*{Acknowledgements}
We would like to thank the anonymous referees for their valuable suggestions. We thank 
Evgeny Kapun for his suggestions regarding the undecidability proof.
